---
title: "Untitled"
author: "Samuel Burkart"
date: "10/4/2021"
output: 
  html_document:
  theme: united
  code_folding: 'hide'
  keep_md: true
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(gridExtra)
diamonds
?diamonds
#Make visualizations to give the distribution of each of the x, y, and z variables in the diamonds data set.

plot1 <- ggplot(diamonds, aes(x=x)) + 
  geom_histogram() +
    labs(title = "Distribution of length in mm")
plot1


plot2 <- ggplot(diamonds, aes(x=y)) + 
  geom_histogram() +
    labs(title = "Distribution of width in mm")
plot2


plot3 <- ggplot(diamonds, aes(x=z)) + 
  geom_histogram() +
    labs(title = "Distribution of depth in mm")
plot3

```

```{r}
#Explore the distribution of price. Is there anything unusual or surprising?
plot4 <- ggplot(diamonds, aes(x = price)) + 
  geom_histogram() +
      labs(title = "Distribution of price")
plot4
```
It is unusual as the distribution for price is very right skewed. 

```{r}
#Can you determine what variable in the diamonds dataset is most important for predicting the price of a diamond? How is that variable correlated with cut? Why does the combination of those two relationships lead to lower quality diamonds being more expensive?
plot5 <- ggplot(diamonds, aes(x=carat, y=price)) + geom_point() + geom_smooth(se=FALSE) +
      labs(title = "The Trend of Price in Relation to Carat Size")

plot5
```
We can see based off the graphic above that carat is the most important variable for predicting the price of a diamond.

```{r}
plot6 <- ggplot(diamonds, aes(x=carat, y=price, color=cut)) + 
  geom_point() +
      labs(title = "The Level of Cut by Number of Carats")
plot6
```
The lower the amount of carats the better the cut is.

```{r}
plot7 <- ggplot(diamonds, aes(x=carat, y=price, color=clarity)) + 
  geom_point() +
      labs(title = "The Level of Clarity by Number of Carats")
plot7
```
These relationships show us that the lower quality diamonds are the higher carat diamonds. The lower the carat the higher the quality of the diamond.The price goes up as the number of carats goes up. So we can conclude that the lower quality diamonds will be more expensive.

```{r}
#Make a visualization of carat partitioned by price.
price_diamonds <- diamonds %>%
  mutate(groupprice = 
           case_when(
             price>=0 & price <= 2000 ~ "1-2000",
             price>=2001 & price <= 4000 ~ "2001-4000",
             price>=4001 & price <= 6000 ~ "4001-6000",
             price>=6001 & price <= 8000 ~ "6001-8000",
             price>=8001 & price <= 10000 ~ "8001-10000",
             price>=10001 & price <= 12000 ~ "10001-12000",
             price>=12001 & price <= 14000 ~ "12001-14000",
             price>=14001 & price <= 16000 ~ "14001-16000",
             price>=16001 & price <= 18000 ~ "16001-18000",
             price>=18001 & price <= 20000 ~ "18001-20000"),
         groupprice = fct_relevel(groupprice,
"1-2000","2001-4000","4001-6000","6001-8000","8001-10000","10001-12000","12001-14000","14001-16000","16001-18000","18001-20000"))

head(price_diamonds)



plot8 <- ggplot(price_diamonds, aes(x = groupprice, y = carat, fill = groupprice)) +
  geom_boxplot() +
  coord_flip() +
  theme_bw() +
  labs(title = "The number of carats in each group of prices")
plot8

```

```{r}
plot9 <- diamonds %>% 
  filter(carat>=4.0) %>%
  group_by(carat) %>% 
  ggplot(aes(x = price)) +
  geom_histogram() +
  theme_bw() +
  labs(title = "The Price of Very Large Diamonds")

#Then compare the price of small diamonds to large diamonds 
plot10 <- diamonds %>% 
  filter(carat<=1.5) %>%
  group_by(carat) %>% 
  ggplot(aes(x = price)) +
  geom_histogram() +
  theme_bw() +
  labs(title = "The Price of Very Small Diamonds")


grid.arrange(plot9,plot10, nrow=2)
```
The number of big diamonds is far less than the number of small diamonds. Additionally, the number of small diamonds are far less expensive as the carat size determines the weight. The larger diamonds have more carats, and are more expensive. I expected this because we already knew the carats determine the price.

```{r}
plot11 <- ggplot(diamonds, aes(x = price, y = carat)) + 
  geom_col() +
  facet_wrap(~cut, ncol=5) +
  theme_bw() +
  coord_cartesian(ylim = c(0, 12), expand = TRUE) +
  labs(title = "Visualization of Cut, Carat, and Price")
plot11
```


