---
title: "CaseStudy9"
author: "Samuel Burkart"
date: "11/2/2021"
output: 
  html_document:
  theme: united
  code_folding: 'hide'
  keep_md: true
---

```{r}
#load in libraries
library(readr)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(foreign)
library(downloader)
```

```{r}
#read in data
my_data <- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/raw/master/sales.csv", my_data, mode = "wb")
my_data <- read_csv(my_data, skip = 0)
head(my_data)

#use US/Mountain

Mtn_Time<- with_tz(my_data, tzone="US/Mountain")
head(Mtn_Time)

#create correct time aggregations
Mtn_Time1 <- Mtn_Time %>%
  mutate(hour = ceiling_date(Time, "hour")) %>%
  mutate(day = ceiling_date(Time, "day")) %>%
  mutate(week = ceiling_date(Time, "week")) %>%
  mutate(month = ceiling_date(Time, "month"))%>%
  mutate(Hour = hour(hour)) %>%
  group_by(Name, Hour) %>%
  summarise(across(Amount,sum))
head(Mtn_Time1)
tail(Mtn_Time1)

```
```{r}
#recommend hours of operation
plot1 <- ggplot(Mtn_Time1, aes(x = Hour, y = Amount, color = Name)) + 
  geom_point() +
  geom_line () +
  facet_wrap(~Name, scales = 'free')+
  labs(x = 'Hour', y = 'Total Sales' , title = 'Sales per Hour') +
  theme_bw()
plot1
```
```{r}
#group_by daily
Mtn_Time2 <- Mtn_Time %>%
  mutate(hour = ceiling_date(Time, "hour")) %>%
  mutate(day = ceiling_date(Time, "day")) %>%
  mutate(week = ceiling_date(Time, "week")) %>%
  mutate(month = ceiling_date(Time, "month"))%>%
  mutate(Day = wday(day)) %>%
  group_by(Name, Day) %>%
  summarise(across(Amount,sum))
head(Mtn_Time2)
tail(Mtn_Time2)
```
```{r}
#plot for days 
plot2 <- ggplot(Mtn_Time2, aes(x = Day, y = Amount, color = Name)) + 
  geom_point() +
  geom_line () +
  facet_wrap(~Name, scales = 'free')+
  labs(x = 'Day', y = 'Total Sales' , title = 'Sales per Day') +
  theme_bw()
plot2
```
```{r}
#group_by weekly
Mtn_Time3 <- Mtn_Time %>%
  mutate(hour = ceiling_date(Time, "hour")) %>%
  mutate(day = ceiling_date(Time, "day")) %>%
  mutate(week = ceiling_date(Time, "week")) %>%
  mutate(month = ceiling_date(Time, "month"))%>%
  mutate(Week = week(week)) %>%
  group_by(Name, Week) %>%
  summarise(across(Amount,sum))
head(Mtn_Time3)
tail(Mtn_Time3)
```
```{r}
#plot for weeks 
plot3 <- ggplot(Mtn_Time3, aes(x = Week, y = Amount, color = Name)) + 
  geom_point() +
  geom_line () +
  facet_wrap(~Name, scales = 'free')+
  labs(x = 'Week', y = 'Total Sales' , title = 'Sales per Week') +
  theme_bw()
plot3
```
```{r}
#group_by monthly
Mtn_Time4 <- Mtn_Time %>%
  mutate(hour = ceiling_date(Time, "hour")) %>%
  mutate(day = ceiling_date(Time, "day")) %>%
  mutate(week = ceiling_date(Time, "week")) %>%
  mutate(month = ceiling_date(Time, "month"))%>%
  mutate(Month = month(month)) %>%
  group_by(Name, Month) %>%
  summarise(across(Amount,sum))
head(Mtn_Time4)
tail(Mtn_Time4)
```
```{r}
#plot for months 
plot4 <- ggplot(Mtn_Time4, aes(x = Month, y = Amount, color = Name)) + 
  geom_point() +
  geom_line () +
  facet_wrap(~Name, scales = 'free')+
  labs(x = 'Month', y = 'Total Sales' , title = 'Sales per Month') +
  theme_bw()
plot4
```
```{r}
#total sales
total_sales <- Mtn_Time %>%
  mutate(hour = ceiling_date(Time, "hour")) %>%
  mutate(day = ceiling_date(Time, "day")) %>%
  mutate(week = ceiling_date(Time, "week")) %>%
  mutate(month = ceiling_date(Time, "month"))%>%
  group_by(Name) %>%
  summarise(across(Amount,sum))
head(total_sales)
```
```{r}
#total sales plot
plot5 <- ggplot(total_sales, aes(x = Name, y = Amount, fill = Name)) + 
  geom_col()+
  labs(x = 'Company Name', y = 'Total Sales' , title = 'Total Sales per Company') +
  theme_bw()
plot5
```
I would recommend that HotDiggity be the company we invest in. They have proven that they are the best company over this 3 month period as their total sales were the highest of any company. Additionally, HotDiggity had the most concentrated sales for a specific time of day. This means they could potentially stay open for a shorter amount of time, thus reducing their cost. This would lead to greater revenue. 

