---
title: "Task2RBasics"
author: "Samuel Burkart"
date: "8/31/2021"
output:
  html_document:
    theme: cerulean
    keep_md: TRUE
---
#Packages
```{r}
library(knitr)
```

#Computations
```{r}
sin(pi/4)
```

```{r}
x <- 10/3
```
###my_list = list(c('Barry', Sam, Dave, 'Charles')) Sam and Dave are not allowed because they are not in quotation marks. 

```{r}
MySequence <- seq(1,50,7)
MySequence
```

```{r}
my_vector <- c(1,5,12,31,19)
my_vector
```

```{r}
7 + 5 == 12
```
#	== tests if something is identically the same

```{r}
(7+4 = 12)|(5-4 = 1)
```
#You get this error because 7+4 equals 11


#Exercise 1: The assignment variable is different than the variable they called

#Exercise 2:
```{r}
library(tidyverse)

ggplot(dota = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

fliter(mpg, cyl = 8)
filter(diamond, carat > 3)
```
#dota is supposed to be data in line 3. fliter is supposed to be filter in line 6 of the code
```{r}
library(tidyverse)

ggplot(data = mpg) + 
  geom_point(mapping = aes(x = displ, y = hwy))

filter(mpg, cyl == 8)
filter(diamonds, carat > 3)
```

#Tools -> Keyboard Shortcuts Help
