---
title: "CaseStudy7"
author: "Samuel Burkart"
date: "10/11/2021"
output: 
  html_document:
  theme: united
  code_folding: 'hide'
  keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#load libraries and read in the data
library(readr)
library(haven)
library(readxl)
library(ggplot2)
library(tidyverse)
library(foreign)
library(downloader)

male_height_dataXLSX <- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/blob/master/Height.xlsx?raw=true", male_height_dataXLSX, mode = "wb")
male_height_dataXLSX <- read_xlsx(male_height_dataXLSX, skip = 2)

head(male_height_dataXLSX)

male_height_dataDTA<- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/blob/master/germanconscr.dta?raw=true", male_height_dataDTA, mode = "wb")
male_height_dataDTA <- read_dta(male_height_dataDTA)

head(male_height_dataDTA)

male_height_dataDTA2<- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/blob/master/germanprison.dta?raw=true", male_height_dataDTA2, mode = "wb")
male_height_dataDTA2 <- read_dta(male_height_dataDTA2)

head(male_height_dataDTA2)

male_height_dataDBF<- tempfile()
download("https://github.com/WJC-Data-Science/DTS350/blob/master/Heights_south-east/B6090.DBF?raw=true", male_height_dataDBF, mode = "wb")
male_height_dataDBF <- read.dbf(male_height_dataDBF, as.is = FALSE)

head(male_height_dataDBF)

male_height_dataCSV <- tempfile()
download("https://raw.githubusercontent.com/hadley/r4ds/master/data/heights.csv", male_height_dataCSV, mode = "wb")
male_height_dataCSV <- read_csv(male_height_dataCSV)
head(male_height_dataCSV)

head(male_heigh_dataCSV)

male_height_dataSAV <- tempfile()
download("http://www.ssc.wisc.edu/nsfh/wave3/NSFH3%20Apr%202005%20release/main05022005.sav", male_height_dataSAV, mode = "wb")
male_height_dataSAV <- read_sav(male_height_dataSAV)

head(male_height_dataSAV)


#tidy the data

worlddata <- male_height_dataXLSX %>%  pivot_longer(3:203, names_to = "years", values_to = "heights.cm", values_drop_na = TRUE) %>%  mutate(year_decade = years, 
         height.in = heights.cm/2.54) %>%  separate(years, into = c("century", "decade"), sep = -2) %>%  separate(decade, into = c("decade", "year"), sep = -1)

head(worlddata)

germany_height <- worlddata %>% 
  filter(`Continent, Region, Country` == "Germany")

chett1 <- male_height_dataDTA %>%  mutate(birth_year = bdec, 
         height.cm = height, 
         height.in = height.cm/2.54, 
         study.id = "male_height_dataDTA") %>%  select(birth_year, height.cm, height.in, study.id)

head(chett1)

chett2 <- male_height_dataDTA2 %>%
  mutate(birth_year = bdec,
         height.cm = height,
         height.in = height.cm/ 2.54,
         study.id = "male_height_dataDTA2") %>%
  select(birth_year, height.in, height.cm, study.id)

head(chett2)

chett3 <- male_height_dataDBF %>%  mutate(height.in = CMETER/2.54,
         height.cm = CMETER,
         birth_year = SJ,
         study.id = "male_height_dataDBF") %>%  select(height.in, height.cm, birth_year, study.id)

head(chett3)

chett4 <- male_height_dataCSV %>%  mutate(birth_year = 1950,
         height.in = height,
         height.cm = height.in*2.54,
         study.id = "male_height_dataCSV") %>%  select(birth_year, height.cm, height.in, study.id)

head(chett4)

chett5 <- male_height_dataSAV %>%  mutate(birth_year = DOBY + 1900, 
                                study.id = "male_height_dataSAV") %>%  select(birth_year, study.id)

head(chett5)

#combine them into one tidy data set
charty <- bind_rows(chett1, chett2, chett3, chett4, chett5)

head(charty)


#make a plot w decade on the x-axis and height in inches on the y-axis
plot1 <- worlddata %>% 
  ggplot(aes(x = year_decade, y = height.in)) +
  geom_point() +
  geom_point(data=germany_height, color = "orange") +
  theme_bw() 
plot1

#make small-multiples plot
plot2 <-  charty %>%
  ggplot(aes(x = birth_year, y = height.in, color = height.in)) +
  geom_col() +
  facet_wrap(~study.id, scales = "free") 
plot2
```
The driving question which "The Scientific American" answers is "Are humans getting taller over the years?". In our plot 1, we show how height in inches is increasing by each decade. This is especially apparent when we analyze the height of Germany which is shown in orange. Throughout time, the trend of height is consistently rising. When we look at plot 2, the trend of height is unclear throughout time. 


