---
title: "Task4"
author: "Samuel Burkart"
date: "9/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load Packages and read in the data. Create a tibble.
```{r}
library(tidyverse)
iris_data <- iris 

tibble(iris_data)
```

#arrange the iris data by Sepal.Length
```{r}
arrange_Sepal.Length <- arrange(iris_data, Sepal.Length)
head(arrange_Sepal.Length, 10)
```

#Select Species and Petal.Width 
```{r}
testdat <- select(iris_data, Species, Petal.Width)

```

#Create species_mean
```{r}
species_mean <- group_by(iris_data, Species)
species_mean <- summarize(species_mean, v1 = mean(Sepal.Length), v2 = mean(Sepal.Width), 
                                                          v3 = mean(Petal.Length),
                                                          v4 = mean(Petal.Width))
species_mean
```

#Create iris_min
```{r}
iris_min <- filter(iris_data, Sepal.Width >= 3, Petal.Width != 2.5)
head(iris_min)
```

#Create iris_size
```{r}
iris_size <- iris_data %>%
  mutate(Sepal.Size = 
           case_when(
             Sepal.Length < 5 ~ "small",
             Sepal.Length >= 5 & Sepal.Length < 6.5 ~ "medium",
             Sepal.Length >= 6.5 ~ "large"))
head(iris_size)   
```

#Create iris_rank
```{r}
iris_rank <- iris_data %>%
  arrange(desc(Petal.Length))
head(iris_rank)
```

#Use summarise_all()
```{r}
?summarise_all
means_sd_species <- iris_data %>%
  group_by(Species) %>%
  summarize_all(list(Mean=mean, Std_dev = sd))

means_sd_species
```


#Report:
#Question 1: Is Uber making NYC rush hour traffic worse?
#Question 2: How to predict restaurant success? 
#Question 3: How to detect fake news?

#Summary from 5 people: These handful of people seem relatively interested in my questions. The most inerest was in question 3.

#Present your question to a professional: I do not know any professionals in these fiels and I do not have access to the people who have answered these questions.  