---
title: "Task22"
author: "Samuel Burkart"
date: "11/22/2021"
output: html_document
---

```{r}
library(tidyverse)
library(downloader)
library(readxl)
```

```{r}
SoloData <- read_csv("solo-artist-followers.csv")
BillboardData <- read_csv("billboard-hits.csv")
view(SoloData)
view(BillboardData)
str(SoloData)
str(BillboardData)

#Change peak_date to column date
BillboardData <- read_csv(
  ("billboard-hits.csv"),
col_types = cols(
  peak_date = col_date("%m/%d/%y")
  )
)
head(BillboardData)
str(BillboardData)
view(BillboardData)
```
#The data types imported correctly as characters.

```{r}
top_six <- BillboardData %>%
  group_by(name) %>%
  filter(n() > 6, band != "")
view(top_six)
```
#This removed about 50 entries from the data set.

```{r}
top_bands <- BillboardData %>%
  group_by(band) %>%
  filter(name %in% top_six$band)
head(top_bands)
#Switch band names with the name data.
top_bands <-rename(top_bands, band = name, name = band)
head(top_bands)
view(top_bands)
```


```{r}
ggplot(data = top_six, aes(x = peak_date, y = peak_rank, color = name, group = name)) +
  geom_point() +
  geom_line() +
  geom_point(data = top_bands, color ="black") +
  geom_line(data = top_bands, color = "black", linetype = "dotted") +
  facet_wrap(~ band, scales = "free") +
  xlab("peak_rank") + ylab("peak_rank") +
  theme_bw() +
  labs(title = 'Year: {peak_date}', x = 'GDP per capita', y = 'peak_rank') +
  transition_time(year) +
  ease_aes('linear') 